---
title: "Study_3_observational"
author: "Anne"
date: "12/20/2021"
output: html_document
---

# III Observational


```{r include=F}
library(stringr)
library(zoo)
library(lubridate)
library(sjlabelled)

# rename columns T1 
observational <- observational_finstrain
observational_T2 <- observational_finstrain_T2

names(observational) <- paste0("T1",names(observational))
names(observational) <- gsub("quit1_1", "quitint_1", names(observational))
names(observational) <- gsub("quit2_1", "quitint_2", names(observational))
names(observational) <- gsub("quit2_2", "quitint_3", names(observational))
names(observational) <- gsub("(PANA)_([6-9]|10)", "PA_\\2", names(observational))
names(observational) <- gsub("(PANA_)([1-5])", "NA_\\2", names(observational))

names(observational_T2) <- gsub("quit_1_1", "quitint_1", names(observational_T2))
names(observational_T2) <- gsub("quit_2_1", "quitint_2", names(observational_T2))
names(observational_T2) <- gsub("quit_2_2", "quitint_3", names(observational_T2))

III_observational_df_raw_full <- left_join(observational, observational_T2, by = c("T1PROLIFIC_PID" = "PROLIFIC_PID"))

III_observational_df_raw_full$ID <- seq.int(nrow(III_observational_df_raw_full))


```

```{r}
# raw data 
III_observational_df_raw <- III_observational_df_raw_full %>%
  dplyr::select(matches("ID|occ$|T1finstrain|T2_quitint|T1concom|T1affcom|coown|found|employees|year|month|edu$|lang$|timebuiss|T2_quitfinstrain$")) 

write.csv(III_observational_df_raw,"../03_Data/raw_data/III_observational_df_raw.csv", row.names = FALSE)
```


```{r}
library(labelled)
CodeBook <-
as.data.frame(rbind(
  c("T1occ",
    var_label(III_observational_df_raw$T1occ),
    paste(get_labels(III_observational_df_raw$T1occ, values = "p"), collapse = ", ")
  ),
 c("T1finstrain_1",
    var_label(III_observational_df_raw$T1finstrain_1),
    paste(get_labels(III_observational_df_raw$T1finstrain_1, values = "p"), collapse = ", ")
  ),
 c("T1finstrain_2",
    var_label(III_observational_df_raw$T1finstrain_2),
    paste(get_labels(III_observational_df_raw$T1finstrain_2, values = "p"), collapse = ", ")
  ),
 c("T1finstrain_3",
    var_label(III_observational_df_raw$T1finstrain_3),
    paste(get_labels(III_observational_df_raw$T1finstrain_3, values = "p"), collapse = ", ")
  ),
 c("T1concom_1",
    var_label(III_observational_df_raw$T1concom_1),
    paste(get_labels(III_observational_df_raw$T1concom_1, values = "p"), collapse = ", ")
  ),
 c("T1concom_2",
    var_label(III_observational_df_raw$T1concom_2),
    paste(get_labels(III_observational_df_raw$T1concom_2, values = "p"), collapse = ", ")
  ),
 c("T1concom_3",
    var_label(III_observational_df_raw$T1concom_3),
    paste(get_labels(III_observational_df_raw$T1concom_3, values = "p"), collapse = ", ")
  ),
 c("T1affcom_1",
    var_label(III_observational_df_raw$T1affcom_1),
    paste(get_labels(III_observational_df_raw$T1affcom_1, values = "p"), collapse = ", ")
  ),
 c("T1affcom_2",
    var_label(III_observational_df_raw$T1affcom_2),
    paste(get_labels(III_observational_df_raw$T1affcom_2, values = "p"), collapse = ", ")
  ),
 c("T1affcom_3",
    var_label(III_observational_df_raw$T1affcom_3),
    paste(get_labels(III_observational_df_raw$T1affcom_3, values = "p"), collapse = ", ")
 ),
 c("T1year_1",
    var_label(III_observational_df_raw$T1year_1),
    paste(get_labels(III_observational_df_raw$T1year_1, values = "p"), collapse = ", ")
 ),
 c("T1month_1",
    var_label(III_observational_df_raw$T1month_1),
    paste(get_labels(III_observational_df_raw$T1month_1, values = "p"), collapse = ", ")
 ),
 c("T1found",
    var_label(III_observational_df_raw$T1found),
    paste(get_labels(III_observational_df_raw$T1found, values = "p"), collapse = ", ")
 ),
 c("T1employees",
    var_label(III_observational_df_raw$T1employees),
    paste(get_labels(III_observational_df_raw$T1employees, values = "p"), collapse = ", ")
 ),
 c("T1coown",
    var_label(III_observational_df_raw$T1coown),
    paste(get_labels(III_observational_df_raw$T1coown, values = "p"), collapse = ", ")
 ),
  c("T1lang",
    var_label(III_observational_df_raw$T1lang),
    paste(get_labels(III_observational_df_raw$T1lang, values = "p"), collapse = ", ")
 ),
  c("T1edu",
    var_label(III_observational_df_raw$T1edu),
    paste(get_labels(III_observational_df_raw$T1edu, values = "p"), collapse = ", ")
 ),
  c("T2_occ",
    var_label(III_observational_df_raw$T2_occ),
    paste(get_labels(III_observational_df_raw$T2_occ, values = "p"), collapse = ", ")
 ),
  c("T2_quitfinstrain",
    var_label(III_observational_df_raw$T2_quitfinstrain),
    paste(get_labels(III_observational_df_raw$T2_quitfinstrain, values = "p"), collapse = ", ")
 ),
  c("T2_quitint_1",
    var_label(III_observational_df_raw$T2_quitint_1),
    paste(get_labels(III_observational_df_raw$T2_quitint_1, values = "p"), collapse = ", ")
 ),
  c("T2_quitint_2",
    var_label(III_observational_df_raw$T2_quitint_2),
    paste(get_labels(III_observational_df_raw$T2_quitint_2, values = "p"), collapse = ", ")
 ),
  c("T2_quitint_3",
    var_label(III_observational_df_raw$T2_quitint_3),
    paste(get_labels(III_observational_df_raw$T2_quitint_3, values = "p"), collapse = ", ")
 )
)
)

names(CodeBook) <- c("Variable name", "Description", "Values")

write.csv(CodeBook,"../02_Research_materials/Codebooks/III_observational_CodeBook.csv", row.names = FALSE)
```

## PREPROCESSING START 

### Recode

```{r include=F}
# recode columns
III_observational_df_raw_full <- III_observational_df_raw_full %>% 
  dplyr::mutate_at(vars(dplyr::matches(c("employable_2", "affcom_1", "affcom_2"))), ~ (.*(-1)+6)) %>% 
  dplyr::mutate(T2_jobsat_1 =  T2_jobsat_1*(-1)+7)


# remove test data
III_observational_df_raw_full <- subset(III_observational_df_raw_full, nchar(as.character(III_observational_df_raw_full$T1PROLIFIC_PID)) >= 15) %>% drop_na(T1occ)

# make age 
III_observational_df_raw_full$T1age_1 <- as.numeric(names(attr(III_observational_df_raw_full$T1age_1,"labels")[match(III_observational_df_raw_full$T1age_1,attr(III_observational_df_raw_full$T1age_1,"labels"))]))


# make time since business foundation
timediff <- function() {
  year_n <- as.numeric(names(attr(III_observational_df_raw_full$T1year_1,"labels")[match(III_observational_df_raw_full$T1year_1,attr(III_observational_df_raw_full$T1year_1,"labels"))]))
  month_n <- as.numeric(III_observational_df_raw_full$T1month_1 %>% remove_all_labels(.))
  time <- as.yearmon(paste(year_n, month_n), "%Y %m") %>% as_date(.)
  record <- as.yearmon(III_observational_df_raw_full$T1RecordedDate, "%Y %m") %>% as_date(.)
  difftime <- difftime(record, time, UTC,
         units = c("days"))
  return(difftime)
}

III_observational_df_raw_full$T1timebuiss <- timediff()


# deselect not important columns
III_observational_df_raw_full <- III_observational_df_raw_full  %>%
dplyr::select(-dplyr::matches("Always|bye|group|Status|IPAddress|Progress|Duration|Finished|ResponseId|
                                                         LastName|FirstName|entEmail|Reference|Latitude|Longitude|Channel|UserLang|
                                                         Consent|Q28"))

# Replace occ status
III_observational_df_raw_full <- III_observational_df_raw_full %>% remove_all_labels(.) %>%
     mutate(T1occ = case_when(T1occ_3_TEXT=="Business owner but main role is home maker|Business owner and student|Student with business
                            |student business owner|self employed and carer for my daughter|Self-employed and student"~ 2,
                            TRUE ~ T1occ))

# check for duplicates
III_observational_df_raw_full <- III_observational_df_raw_full[!(duplicated(III_observational_df_raw_full$T1PROLIFIC_PID)), ]
```



### Sample overviews

```{r include=TRUE}
# remove not entrepreneur
III_observational_df_raw_full<- III_observational_df_raw_full %>% drop_na(T1occ)
III_observational_df_raw_full <- III_observational_df_raw_full[!(III_observational_df_raw_full$T1occ ==3), ]
names(III_observational_df_raw_full) <- gsub(x = names(III_observational_df_raw_full), pattern = "T2_", replacement = "T2")

# delete not involved in founding
cat("Number of participants not involved in founding removed:", nrow(III_observational_df_raw_full[(III_observational_df_raw_full$T1found ==2), ]), "\n")
III_observational_df_raw_full <- III_observational_df_raw_full[!(III_observational_df_raw_full$T1found ==2), ]

```

```{r}
orig_df <- III_observational_df_raw_full
```

```{r include=TRUE}
# basis sample (no filters)
III_observational_df_raw_full<- III_observational_df_raw_full %>% drop_na(T1occ)
cat("Number of entrepreneurs at T1:", nrow(III_observational_df_raw_full), "\n")

# Dropouts 
III_observational_df_raw_full_noT2 <- III_observational_df_raw_full %>% drop_na(T2quitint_1, T2quitint_2, T2quitint_3)
cat("Drop out from T1 to T2: ", nrow(III_observational_df_raw_full) - nrow(III_observational_df_raw_full_noT2), "\n")
cat("Percentage Drop out from T1 to T2: ", ((nrow(III_observational_df_raw_full) - nrow(III_observational_df_raw_full_noT2))/ nrow(III_observational_df_raw_full)), "\n")
III_observational_df_raw_full <- III_observational_df_raw_full_noT2

# basis sample after dropouts removed
# Drop NA on model variables
cat("Number of participants who provided data at T1 and T2:", nrow(III_observational_df_raw_full), "\n")


# Quit between last survey and now
cat("Number of T2 participants who quit their business between May 2021 and now (Dec 2021): ", nrow(III_observational_df_raw_full[(III_observational_df_raw_full$T2quit ==2), ]), "\n")
III_observational_df_raw_full <- III_observational_df_raw_full[!(III_observational_df_raw_full$T2quit ==2), ]


# Attention checks T1
## create attention fails df 
attention_fail <- function() {
  attention_f <- III_observational_df_raw_full[(III_observational_df_raw_full$T1chal_3 != 4) | (III_observational_df_raw_full$T1threat_4 != 4) | (III_observational_df_raw_full$T1satis_4 != 2),]
  ID_vals <- data.frame(table(attention_f$T1ID))
  Rows_fails <- attention_f$T1ID %in% ID_vals[ID_vals$Freq > 0,1]
  Att_fails <- attention_f[Rows_fails,]
  return(Att_fails)
}

Att_fails <- attention_fail() # 8 excluded

## exclude attention fails (one or more fails)
t1 <- III_observational_df_raw_full %>% dplyr::select(-dplyr::matches("T2")) %>% drop_na(T1occ) %>% .[!(.$T1ID %in% Att_fails$T1ID),] %>% dplyr::select(-T1chal_3,-T1threat_4,-T1satis_4)

cat("Number of T1 attention fails (at least one of three attention check items failed):", nrow(Att_fails) , "\n")
# Number of T2 participants
t2 <- III_observational_df_raw_full[!(is.na(III_observational_df_raw_full$T2PID)), ] %>% dplyr::select(dplyr::matches("T2"))

### Attention checks T2
## create attention fails df 
attention_fail <- function() {
  attention_f <- t2[(t2$T2lifesat_4 != 2) | (t2$T2vita_5 != 3) | (t2$T2entresat_4 != 6),]
  ID_vals <- data.frame(table(attention_f$T2_PID))
  Rows_fails <- attention_f$T2PID %in% ID_vals[ID_vals$Freq > 0,1]
  Att_fails <- attention_f[Rows_fails,]
  return(Att_fails)
}

Att_fails <- attention_fail() 

## exclude attention fails (one or more fails)
t2<- t2 %>% .[!(.$T2PID %in% Att_fails$T2PID),] %>% dplyr::select(-T2lifesat_4 ,-T2vita_5, -T2entresat_4)

cat("Number of T2 attention fails (at least one of three attention check items failed):", nrow(Att_fails) , "\n")


# join the two attention checked data frames 
III_observational_df_raw_full <- left_join(t1, t2, by = c("T1PROLIFIC_PID" = "T2PID"))

# NA on model variables
# assign NA to non-binary defined
III_observational_df_raw_full$T1gender[III_observational_df_raw_full$T1gender ==3] = NA
III_observational_df_raw_full_nona <- III_observational_df_raw_full %>% drop_na(T1gender, T1age_1, T1timebuiss)
cat("No response on model variables: ", nrow(III_observational_df_raw_full) - nrow(III_observational_df_raw_full_nona), "\n")

III_observational_df_raw_full<- III_observational_df_raw_full_nona 

cat("Final sample size: ", nrow(III_observational_df_raw_full), "\n")
```

## PREPROCESSING END 


```{r}
III_observational_df_preproc <- III_observational_df_raw_full %>%
  dplyr::select(matches("ID|occ|employees|coown|indu|locat|age_1|gender|lang|edu|timeb|quitfinstrain|T2currententre|T2quit|finstrain_\\d$|quitint|affcom|concom")) 
## preprocessed dataset 
write.csv(III_observational_df_preproc,"../03_Data/preprocessed_data/III_observational_df_preproc.csv", row.names = FALSE)
```

## Participant characteristics

```{r}
set.seed(42)
  library(qwraps2)
# define the markup language we are working in.
# options(qwraps2_markup = "latex") is also supported.
options(qwraps2_markup = "markdown")
```


```{r include = TRUE}
tabyl(III_observational_df_preproc$T1gender)

# Age overview
cat("Range age: ", range(III_observational_df_preproc$T1age_1,  na.rm = T))

cat(paste0(" Mean (SD) age: ", round(mean(III_observational_df_preproc$T1age_1, na.rm = T), 1), " (", round(sd(III_observational_df_raw_full$T1age_1, na.rm = T), 1), ")"))

# Business age overview 
III_observational_df_preproc$T1timebuiss <- III_observational_df_preproc$T1timebuiss/365
cat(" Range business age (in years): ", range(III_observational_df_preproc$T1timebuiss,  na.rm = T))
cat(paste0(" Mean (SD) business age: ", round(mean(III_observational_df_preproc$T1timebuiss, na.rm = T), 1), " (", round(sd(III_observational_df_preproc$T1timebuiss, na.rm = T), 1), ")"))

# Coownership
tabyl(III_observational_df_preproc$T1coown)

# Industry 

# 1 Information, Communications, or Technology
# 2 Finance, Real Estate, or Business Services
# 3 Health, Education, Government, or Social and Consumer Services
# 4 Wholesale, Retail
# 5 Manufacturing, Logistics
# 6 Agriculture, Extractive, or Construction
# 7 Other, namely:
III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Jewellery" | III_observational_df_preproc$T1indu_7_TEXT == "food service", 4, III_observational_df_preproc$T1indu)

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Writing services" | III_observational_df_preproc$T1indu_7_TEXT == "Pet services" | III_observational_df_preproc$T1indu_7_TEXT == "pet" | III_observational_df_preproc$T1indu_7_TEXT == "Personal services" | III_observational_df_preproc$T1indu_7_TEXT == "Services" | III_observational_df_preproc$T1indu_7_TEXT == "hospitality" | III_observational_df_preproc$T1indu_7_TEXT == "Courier and delivery" |  III_observational_df_preproc$T1indu_7_TEXT == "translation" | III_observational_df_preproc$T1indu_7_TEXT == "cleaning" |  III_observational_df_preproc$T1indu_7_TEXT == "legal" |  III_observational_df_preproc$T1indu_7_TEXT == "law" | III_observational_df_preproc$T1indu_7_TEXT == "Teaching sewing, alterations, dressmaking,  sewing" | III_observational_df_preproc$T1indu_7_TEXT == "Hospitality" | III_observational_df_preproc$T1indu_7_TEXT == "Food" | III_observational_df_preproc$T1indu_7_TEXT == "Maintenance" | III_observational_df_preproc$T1indu_7_TEXT == "Health" | III_observational_df_preproc$T1indu_7_TEXT == "taxi" | III_observational_df_preproc$T1indu_7_TEXT == "Sports Coaching" | III_observational_df_preproc$T1indu_7_TEXT == "Wellbeing" | III_observational_df_preproc$T1indu_7_TEXT == "Tourism" | III_observational_df_preproc$T1indu_7_TEXT == "Fitness" | III_observational_df_preproc$T1indu_7_TEXT == "Complementary therapy" | III_observational_df_preproc$T1indu_7_TEXT == "Hospitality" | III_observational_df_preproc$T1indu_7_TEXT == "hospitality" | III_observational_df_preproc$T1indu_7_TEXT == "[ersonal services" | III_observational_df_preproc$T1indu_7_TEXT == "Legal support and publishing" | III_observational_df_preproc$T1indu_7_TEXT == "Professional Services" | III_observational_df_preproc$T1indu_7_TEXT == "Tourism", 3, III_observational_df_preproc$T1indu)

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Design" | III_observational_df_preproc$T1indu_7_TEXT == "Fine art restoration" | III_observational_df_preproc$T1indu_7_TEXT == "Graphic Design" | III_observational_df_preproc$T1indu_7_TEXT == "Art/Engineering/Photography" |  III_observational_df_preproc$T1indu_7_TEXT == "Arts" | III_observational_df_preproc$T1indu_7_TEXT == "Arts" | III_observational_df_preproc$T1indu_7_TEXT == "Arts/Entertainment" | III_observational_df_preproc$T1indu_7_TEXT == "Events" | III_observational_df_preproc$T1indu_7_TEXT == "Art" | III_observational_df_preproc$T1indu_7_TEXT == "photography and videography" | III_observational_df_preproc$T1indu_7_TEXT == "arts" | III_observational_df_preproc$T1indu_7_TEXT == "Art and design" | III_observational_df_preproc$T1indu_7_TEXT == "Handmade craft" | III_observational_df_preproc$T1indu_7_TEXT == "Entertainment and Arts" | III_observational_df_preproc$T1indu_7_TEXT == "Entertainment" | III_observational_df_preproc$T1indu_7_TEXT == "Illustration" | III_observational_df_preproc$T1indu_7_TEXT == "Printmaking/Bookbinding/Design" | III_observational_df_preproc$T1indu_7_TEXT == "Creative industry" | III_observational_df_preproc$T1indu_7_TEXT == "creative arts" | III_observational_df_preproc$T1indu_7_TEXT == "Design" | III_observational_df_preproc$T1indu_7_TEXT == "Entertainment and events" | III_observational_df_preproc$T1indu_7_TEXT == "Events industry/entertainment" | III_observational_df_preproc$T1indu_7_TEXT == "Decorative" | III_observational_df_preproc$T1indu_7_TEXT == "Literature" | III_observational_df_preproc$T1indu_7_TEXT == "Art and Design" | III_observational_df_preproc$T1indu_7_TEXT == "Arts" | III_observational_df_preproc$T1indu_7_TEXT == "Photography" | III_observational_df_preproc$T1indu_7_TEXT == "Arts and crafts" | III_observational_df_preproc$T1indu_7_TEXT == "Graphic Design" | III_observational_df_preproc$T1indu_7_TEXT == "entertainment" | III_observational_df_preproc$T1indu_7_TEXT == "Design" | III_observational_df_preproc$T1indu_7_TEXT == "personal services, photography" | III_observational_df_preproc$T1indu_7_TEXT == "Art" | III_observational_df_preproc$T1indu_7_TEXT == "Entertainment" | III_observational_df_preproc$T1indu_7_TEXT == "Artisan" | III_observational_df_preproc$T1indu_7_TEXT == "Media", 8, III_observational_df_preproc$T1indu)

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Consulting" | III_observational_df_preproc$T1indu_7_TEXT == "counselling" | III_observational_df_preproc$T1indu_7_TEXT == "Marketing", 2, III_observational_df_preproc$T1indu)

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Industrial design", 6, III_observational_df_preproc$T1indu) 

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Design/luxury items" | III_observational_df_preproc$T1indu_7_TEXT == "retail", 4, III_observational_df_preproc$T1indu)

III_observational_df_preproc$T1indu <- ifelse(III_observational_df_preproc$T1indu_7_TEXT == "Trading", 5, III_observational_df_preproc$T1indu)


III_observational_df_preproc$T1indu_7_TEXT

tabyl(III_observational_df_preproc$T1indu)

# Country 
library(dplyr)
library(zoo)
library(lubridate)
#tabyl(III_observational_df_preproc$T1locat)

III_observational_df_preproc[III_observational_df_preproc$T1indu == 7,]
```

```{r}
library(sjlabelled)
library(data.table)

comp_dat <- III_observational_df_preproc %>%
  dplyr::select(dplyr::matches("finstrain_\\d$|quitint|affcom|concom")) %>% remove_all_labels(.) %>% .[, !sapply(., is.character)]

demo_dat <- III_observational_df_preproc %>%
  dplyr::select(dplyr::matches("ID|occ|employees|coown|indu|locat|age_1|gender|lang|edu|timeb|quitfinstrain|T2currententre|T2quit")) %>% dplyr::select(-dplyr::matches("TEXT")) %>% remove_all_labels(.)

demo_dat$T1timebuiss <- as.numeric(demo_dat$T1timebuiss)

alph_dat <- comp_dat

comp_split <- comp_dat %>%
  split.default(sub("_.*", "", names(comp_dat))) 

alph_split <- alph_dat %>%
  split.default(sub("_.*", "", names(alph_dat))) 

comp <- purrr::map(comp_split, ~ rowMeans(.x), data = .x) %>% as.data.frame(.)
alph <- purrr::map(alph_split, ~ psych::alpha(.x), data = .x) %>%
  purrr::map(~ .x$total)

# add demos
comp_df <- cbind(comp, demo_dat) %>% .[, !sapply(., is.character)]

alph_df <- do.call("rbind", alph) %>% round(., 2)
```

## Robustness check 

```{r}
comp_dat <- orig_df %>%
  dplyr::select(dplyr::matches("finstrain_\\d$|quitint|affcom|concom")) %>% remove_all_labels(.) %>% .[, !sapply(., is.character)]

demo_dat <- orig_df %>%
  dplyr::select(dplyr::matches("ID|occ|employees|coown|indu|locat|age_1|gender|lang|edu|timeb|quitfinstrain|T2currententre|T2quit")) %>% dplyr::select(-dplyr::matches("TEXT")) %>% remove_all_labels(.)


alph_dat <- comp_dat

comp_split <- comp_dat %>%
  split.default(sub("_.*", "", names(comp_dat))) 

alph_split <- alph_dat %>%
  split.default(sub("_.*", "", names(alph_dat))) 

comp <- purrr::map(comp_split, ~ rowMeans(.x), data = .x) %>% as.data.frame(.)
alph <- purrr::map(alph_split, ~ psych::alpha(.x), data = .x) %>%
  purrr::map(~ .x$total)

# add demos
comp_df_robust <- cbind(comp, demo_dat) %>% .[, !sapply(., is.character)]

alph_df <- do.call("rbind", alph) %>% round(., 2)
```


```{r}
## Robustness check
df_drop <- comp_df_robust[!comp_df_robust$ID %in% comp_df$ID,]


# AGE
t.test(df_drop$T1age_1, comp_df$T1age_1, alternative = "two.sided", var.equal = FALSE)

# GENDER
df_drop <- df_drop %>% naniar::replace_with_na(replace = list(T1gender = 3))
gender_table <- rbind(table(df_drop$T1gender), table(comp_df$T1gender))
# Perform chi-square test
chisq_test <- chisq.test(gender_table)
# Print the result
print(chisq_test)

# COOWN 
coown_table <- rbind(table(df_drop$T1coown), table(comp_df$T1coown))
# Perform chi-square test
chisq_test <- chisq.test(coown_table)
# Print the result
print(chisq_test)


# BUSINESS AGE
df_drop$T1timebuiss <- as.numeric(df_drop$T1timebuiss)
df_drop$T1timebuiss <- df_drop$T1timebuiss/365
t.test(df_drop$T1timebuiss, comp_df$T1timebuiss, alternative = "two.sided", var.equal = FALSE)

# FINANCIAL STRESS
t.test(df_drop$T1finstrain, comp_df$T1finstrain, alternative = "two.sided", var.equal = FALSE)
sd(df_drop$T1finstrain, na.rm = T)

# AFFECTIVE COMMITMENT 
t.test(df_drop$T1affcom, comp_df$T1affcom, alternative = "two.sided", var.equal = FALSE)
sd(df_drop$T1affcom, na.rm = T)

# CONTINUE COMMITMENT
t.test(df_drop$T1concom, comp_df$T1concom, alternative = "two.sided", var.equal = FALSE)

sd(comp_df$T1finstrain, na.rm = T)
```

```{r}
df_drop$drop <- 1
comp_df$drop <- 0
common_cols <- intersect(colnames(comp_df), colnames(df_drop))
overall_df <- rbind(
  subset(df_drop, select = common_cols), 
  subset(comp_df)
)

model <- glm( drop ~ T1finstrain, data = overall_df, family = binomial)
summary(model)
model <- glm( drop ~ T1affcom, data = overall_df, family = binomial)
summary(model)

```



## Reliabilities 

```{r include = TRUE}
alph_df %>%
DT::datatable(
    extensions = 'Buttons', 
    options = list(dom = 'Bfrtip', 
                   buttons = c('excel', "csv"),
                   pageLength = 15))
```

## Correlations

```{r include = FALSE}
cor <- round(cor(comp_df, use="pairwise.complete.obs"), 2)

library(Hmisc)
library(kableExtra)
res2 <- rcorr(as.matrix(comp_df))
res2$n
corstar_select <- data.frame(corstars(comp_df, removeTriangle = "none", result="none"))

corstar_select %>%
  DT::datatable(
    extensions = 'Buttons', 
    options = list(dom = 'Bfrtip', 
                   buttons = c('excel', "csv"),
                   pageLength = 15,
                  lengthMenu = c(25, 50, 75, 94)))
```

```{r}
names(comp_df)
comp_df_sel <- comp_df %>% dplyr::select(T1affcom, T1concom, T1finstrain, T2quitint, T1age_1, T1gender, T1coown, T1timebuiss)
```


```{r include = TRUE}
library(Hmisc)
comp_df = comp_df_sel  %>% .[, c(3, 1, 2, 5, 6, 7, 8, 4)]

correlation_matrix<-rcorr(as.matrix(comp_df), type="pearson")

#comp_df$T1timebuiss <- comp_df$T1timebuiss/365

## Make table 
Mean <- round(colMeans(comp_df , na.rm =T),2)
SD <- round(apply(comp_df , 2, sd, na.rm =T),2)
mean_sd <- as.data.frame(rbind(Mean, SD)) %>% t()

corstar_select <- cbind(mean_sd, data.frame(corstars(comp_df, removeTriangle = "upper", result="none"))) 



```
```{r}
library(xtable)
print(xtable(corstar_select, type = "latex"), file = "../output/cor_comp_observational.tex")
```



## Factor structure

### 4 separate factors (theoretical model)

```{r include = T}
library(lavaan)
com_FA <- "
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
T1affcom =~ T1affcom_1 + T1affcom_2 + T1affcom_3 
T1concom =~ T1concom_1 + T1concom_2 + T1concom_3 
"
fit <- cfa(com_FA , data=III_observational_df_preproc)
summary(fit, fit.measures=TRUE)
```

### 3 separate factors: quitint & finstrain combined

```{r include = T}
com_FA <- "
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 + T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
T1affcom =~ T1affcom_1 + T1affcom_2 + T1affcom_3 
T1concom =~ T1concom_1 + T1concom_2 + T1concom_3 
"
fit <- cfa(com_FA , data=III_observational_df_preproc)
summary(fit, fit.measures=TRUE)
```

### 3 separate factors: affcom & concom combined

```{r include = T}
com_FA <- "
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
T1affcom =~ T1affcom_1 + T1affcom_2 + T1affcom_3 + T1concom_1 + T1concom_2 + T1concom_3 
"
fit <- cfa(com_FA , data=III_observational_df_preproc)
summary(fit, fit.measures=TRUE)
```



```{r include = F}
### Modification indices > 9
modificationindices(fit) %>%
  as_data_frame() %>%
  arrange(-mi) %>%
  filter(mi > 9) %>%
  select(lhs, op, rhs, mi, epc) %>%
  pander(caption="MI values > 9 for commitment FA")
```



## Hypotheses tests quit intention 

### Step 1

```{r include = TRUE}
library(broom)
model <- '
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
           # direct effect
             T2quitint ~ c*T1finstrain +  control1*T1age_1 + control2*T1gender + control4*T1timebuiss  + control5*T1coown
         '
set.seed(12)
step1 <- sem(model, data = III_observational_df_preproc, se = "bootstrap", bootstrap = 5000) # bootstrap set down to 100 to make estimation faster, 5000 in original  

summary(step1, fit.measures = TRUE)

out_df1 = medmodel(step= step1)


```

### Step 1: Multiple imputation


```{r}
orig_df$T1timebuiss <- as.numeric(orig_df$T1timebuiss)
orig_df$T1timebuiss <- orig_df$T1timebuis/365

imp_df <- orig_df %>% select(-matches("T1consent2|T1occ|T1cope|T1emocope|T1chal|T1threat|T1satis|T1NA|T1PA|T1employable|T1year_1|T1month_1|T1indu|T1locat|T1lang|T1edu|T2Consent|T2lifesat|T2entresat|T2jobsat|ID|T2normcom|T2vita"))

nums <- unlist(lapply(imp_df, is.numeric), use.names = FALSE)  
imp_df <- imp_df[ , nums]

sum(is.na(imp_df$T2quitint_1)) / nrow(imp_df)
```

```{r}
out1 <- semTools::runMI(model, 
              data=imp_df,
              m = 5, 
              miPackage="mice",
              fun="cfa",
              meanstructure = TRUE)
(summary(out1))

summary(out1, ci = TRUE, standardized = T)

anova(out1)
```


### Step 2

```{r include = TRUE}
model <- '
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
T1affcom =~ T1affcom_1 + T1affcom_2 + T1affcom_3 

           # direct effect
             T2quitint ~ c*T1finstrain + control1*T1age_1 + control2*T1gender + control4*T1timebuiss  + control5*T1coown
           # mediator
             T1affcom ~ a1*T1finstrain
             T2quitint ~ b1*T1affcom
           # indirect effect (a*b)
             a1b1 := a1*b1
           # total effect
             total := c + (a1*b1)
         '
set.seed(12)
step2 <- sem(model, data = III_observational_df_preproc, se = "bootstrap", bootstrap = 5000) # bootstrap set down to 100 to make estimation faster, 5000 in original  
out_df2 =  medmodel(step= step2)

step2_fiml <- sem(model, data = imp_df, missing = "fiml", se = "bootstrap", bootstrap = 5000) # bootstrap set down to 100 to make estimation faster, 5000 in original  

summary(step2, fit.measures = TRUE, rsquare=T)
summary(step2_fiml, fit.measures = TRUE)

library(parameters)
model_parameters(
  step2,
  ci = 0.95,
  standardize = FALSE,
  component = c("regression", "correlation", "loading", "defined"),
  keep = NULL,
  drop = NULL,
  parameters = keep,
  verbose = TRUE
)
```

### Step 2: Multiple imputation

```{r}
out2 <- semTools::runMI(model, 
              data=imp_df,
              m = 5, 
              miPackage="mice",
              fun="cfa",
              meanstructure = TRUE)
summary(out2)

summary(out2, ci = TRUE, standardized = T)

anova(out2)
```

### Exploratory: Continuance commitment as mediator 

```{r include = TRUE}
model <- '
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
Tconcom =~ T1concom_1 + T1concom_2 + T1concom_3 

           # direct effect
             T2quitint ~ c*T1finstrain + control1*T1age_1 + control2*T1gender + control4*T1timebuiss  + control5*T1coown
           # mediator
             Tconcom ~ a1*T1finstrain
             T2quitint ~ b1*Tconcom
           # indirect effect (a*b)
             a1b1 := a1*b1
           # total effect
             total := c + (a1*b1)
         '
set.seed(12)
step2_2 <- sem(model, data = III_observational_df_preproc, se = "bootstrap", bootstrap = 5000) # bootstrap set down to 100 to make estimation faster, 5000 in original  
out_df2_2 =  medmodel(step= step2_2)


summary(step2_2, fit.measures = TRUE)

library(parameters)
model_parameters(
  step2_2,
  ci = 0.95,
  standardize = FALSE,
  component = c("regression", "correlation", "loading", "defined"),
  keep = NULL,
  drop = NULL,
  parameters = keep,
  verbose = TRUE
)
```

### Exploratory: Multiple imputation Continuance commitment as mediator 

```{r}
out3 <- semTools::runMI(model, 
              data=imp_df,
              m = 5, 
              miPackage="mice",
              fun="cfa",
              meanstructure = TRUE)

summary(out3, ci = TRUE, standardized = T)

anova(out3)
```


### Exploratory: Continuance and affective commitment as mediators


```{r include = T}
model2 <- '
T2quitint =~ T2quitint_1 + T2quitint_2 + T2quitint_3 
T1finstrain =~ T1finstrain_1 + T1finstrain_2 + T1finstrain_3 
T1affcom =~ T1affcom_1 + T1affcom_2 + T1affcom_3 
T1concom =~ T1concom_1 + T1concom_2 + T1concom_3 


           # direct effect
             T2quitint ~ c*T1finstrain + control1*T1age_1 + control2*T1gender + control4*T1timebuiss  + control5*T1coown
             #T2quitint ~ T1quitint
           # mediator
             T1affcom ~ a1*T1finstrain
             T1concom ~ a2*T1finstrain
             T2quitint ~ b1*T1affcom
             T2quitint ~ b2*T1concom
           # indirect effect (a*b)
             a1b1 := a1*b1
             a2b2 := a2*b2
           # total effect
             total2 := c + (a1 * b1) + (a2 * b2)
             T1affcom ~~ T1concom
         '
set.seed(12)
step3 <- sem(model2, data = III_observational_df_preproc, se = "bootstrap", bootstrap = 5000) # bootstrap set down to 100 to make estimation faster, 5000 in original  
out_df3 =  medmodel(step= step3)
summary(step3, fit.measures = TRUE)

model_parameters(
  step3,
  digits =  "scientific4",
  ci_digits =  "scientific4",
  ci = 0.95,
  standardize = FALSE,
  component = c("regression", "correlation", "loading", "defined"),
  keep = NULL,
  drop = NULL,
  parameters = keep,
  verbose = TRUE
)

parameterEstimates(step3)
```

### Exploratory Multiple imp 

```{r}
out4 <- semTools::runMI(model2, 
              data=imp_df,
              m = 5, 
              miPackage="mice",
              fun="cfa",
              meanstructure = TRUE)

summary(out4, ci = TRUE, standardized = T)

anova(out4)
```














